On the Synchronization Power of the Openflow Data Plane

### 2015-05-20 inband-sync-20-may.tex
Partial commit, still working on Sec 4

\liron{following Petr's comments, I suggest the following paragraph}
At first sight, the Openflow bundle feature seems to provide a simple and generic way for a controller to atomically update switch configuration, similarly to a transaction in shared memory system.
However, while the bundle can indeed be seen
 as a ``mini-transaction'', it comes with several
 limitations, which we discuss in the following.

>>>>

\liron{following Petr's comments (regarding last paragraph), I suggest the following paragraph (instead of the old version which is still in the text before)}
At first sight, the Openflow bundle feature seems to provide a simple and generic way for a controller to atomically update switch configuration, similarly to a transaction in shared memory system.
However, while the bundle can indeed be seen
 as a ``mini-transaction'', it comes with several
 limitations, which we discuss in the following.
